\mythesistitle

### 2011-11-16 src/synopsis.tex
added illustration for v0.2. peanut story and all that. need to complete it - will do by next commit.`

\documentclass[MS]{iitmdiss}

@@

>>>>

\documentclass[MS,]{iitmdiss} 
\usepackage[usenames,dvipsnames]{color}

@@

\chapter{Introduction}
\label{chap:intro}

give some basic gyan about the problem itself? or screw it move to
section directly

\section{Illustration of the problem}
\label{sec:problem}

\def \LLL {{\em ``{\bf L}aughing with Kafka''}} %{Consider the {\bf
                                %L}obster} 
\def \GGG {{\em ``{\bf G}irl with Curious Hair''}} % {``{\bf G}od Bless You,
                                % Mr. Franzen''} 
\def \BBB {{\em ``{\bf B}rief Interviews with Hideous Men''}} %{{\bf B}room
                                %of the System} 
\def \TTT {{\em ``{\bf T}his is Water''}} %{``{\bf T}ennis, Trigonometry,
                                %Tornadoes: A Midwestern  Boyhood''}
                                %%{{\bf T}he Pale King}

\def \Pa {{\em {\bf Pa}tricia}} 
\def \Pi {{\em {\bf Pi}gpen}} %{{\em {\bf Ma}rcie}}
\def \Sn {{\em {\bf Sn}oopy}}
\def \Wo {{\em {\bf Wo}odstock}}
\def \Vi {{\em {\bf Vi}olet}} 
\def \Li {{\em {\bf Li}nus}} 
\def \Ch {{\em {\bf Ch}arlie}}
\def \Sa {{\em {\bf Sa}lly}}
\def \Fr {{\em {\bf Fr}anklin}}  %{{\em {\bf Re}run}} 
\def \Sc {{\em {\bf Sc}hr{\"o}eder}} 
\def \Lu {{\em {\bf Lu}cy}}

\def \residenceblock {{\em Infinite Loop}}

A group of students, \Pa, \Pi, \Sn, \Wo, \Vi, \Li, \Ch, \Sa, \Fr,
  \Sc\ and \Lu\ enroll at the
% {\bf Wo}odstock, {\bf Vi}olet, {\bf Li}nus, {\bf Ch}arlie, {\bf
%   Sa}lly, {\bf Re}run, {\bf Sc}hr{\"o}eder} and {\em {\bf Lu}cy}
% enroll at the
{\em Wallace Studies Institute} for a liberal arts programme.  As part
of their semester thesis, they pick a body of work to study and form
the namesake study groups, {\LLL}, {\GGG}, {\BBB} and {\TTT}. A student
will be in at least one study group and may be in more than one. For
instance, as will be seen later, {\Fr} studies both {\LLL} and {\TTT}
while \Wo\ studies only \BBB.

Let $U$ and $\cF$ represent the set of students and the set of study
groups respectively and the integers $n$ and $m$ denote the total
number students and study groups respectively. In relation to this
example, these are defined as follows. Also given below is the study group
allocation to students. \tnote{use tables}
\tnote{use other font for elements of sets}
\begin{enumerate}[]
\item {$U = \{$Pa,$\; $Pi,$\; $Sn,$\; $Wo,$\; $Vi,$\; $Li,$\; $Ch,$\;
    $Sa,$\; $Fr,$\; $Sc,$\; $Lu$\}$}
\item $\cF = \{L, G, B, T\}$
 % \item ${R = \{g, h, i, j, k\}}$
  % \item ${B = \{a, b, e, g\}}$
  % \item ${O = \{c, b, d\}}$
  % \item ${G = \{e, f , g, i\}}$
\item $L = \{$ Ch,$\; $ Sa,$\; $ Fr,$\; $ Sc,$\; $ Lu $\}$
\item $G = \{$ Pa,$\; $ Pi,$\; $ Vi,$\; $ Ch $\}$
\item $B = \{$ Su,$\; $ Pi,$\; $ Wo $\}$
\item $T = \{$ Vi,$\; $ Li,$\; $ Ch,$\; $ Fr $\}$
\item $n = |U| = 11$, $m = |\cF| = 4$
\end{enumerate}

% The administration faces a small challenge with their
% accommodation. 
The campus has a residential area {\residenceblock} that has $n$
single occupancy apartments reserved for the study groups'
accommodation.  All these apartments are located such that the streets
connecting them do {\em not} form loops. Fig~\ref{fig:streetmap} shows
the street map for {\residenceblock}. It may be noted that as a graph, it
classifies as a tree.

A natural question would be to find how the students should be
allocated apartments such that each study group has the {\em least
  distance to travel} for a discussion? More specifically, we are
interested in enforcing additional conditions, namely, that all the
students in a study group must be next to each other; in other words,
for one student to reach another fellow study group member's apartment
(for all study groups the student is part of), she must not have to
pass the apartment of any student who is not in that study group. To
further elucidate, the apartments of students of any study group must
be arranged in an exclusive unfragmented path on the street
map. Exclusivity here means that the path must not have apartments
from other study groups (unless that apartment is also part of {\em
  this} study group).

An intuitive approach to this problem would be to first find the paths
that each study group decides to inhabit and then refine the
allocation to individual students. One possible allocation of
exclusive routes to study groups is illustrated in
Fig~\ref{fig:streetmap+path}.

\begin{figure}[h]
  % \centering
  (a) \includegraphics[scale=0.3]{../img/a1.pdf}\label{fig:streetmap}
  (b) \includegraphics[scale=0.3]{../img/a2.pdf}\label{fig:streetmap+path}
  \caption{(a) {\residenceblock} street map (b) Street map with study
    group routes allocated. Routes are color coded as follows: red for
    \textcolor{red}{\em \LLL} group, blue for \textcolor{blue}{\em
      \GGG} group, orange for \textcolor{YellowOrange}{\em \BBB} group,
    green for \textcolor{green}{\em \TTT} group}
\end{figure}

\section{Motivation and background}
\label{sec:motivation}

\chapter{Summary of results}
\label{chap:results}
